\documentclass[12pt]{article}
\title{Things to do in RGL}
\begin{document}
\maketitle
\section{Write a paper for JSS}

The paper should come after some of the things below are done; which ones?

\section{Separate window/viewport handling}

We should have a way to control the window size and location.  This will be device-specific. 
We could also handle captions, etc. on the window.

Should it specify locations in a device-independent way (e.g. coordinates running from 0 to 1 on the user screen),
or by pixels?  How are multiple screen systems handled?

Within a window, we should have a way to specify the viewport location, and we should have the
possibility of multiple rgl viewports in the same window.

How are mouse actions handled?  It would be nice to have some flexibility, e.g.
to allow several viewports to be controlled simultaneously, but designing this is tricky. 

\section{A scene graph or tree}

We should maintain a scene as a tree, which can have transformations applied to branches. We should
be able to work with the graph in R, e.g. moving points or changing colours or visibility
of elements without rebuilding the entire graph.

\section{Layers}

We should be able to control the visibility of different elements of a scene.

\section{Navigation versus manipulation}

We don't currently let the viewer move around, we just move the model.  We should allow either
one.

\section{Better transparency}

Could we put all transparent polygons into one big structure so that it could be rendered in back-to-front
order?

\section{Mesh objects}

Mesh objects should allow triangles as well as quads.

\section{Textures and normals }

It should be easier to add texture coordinates and normals to surfaces.

\section{User interaction}

We need a better model for handling user interaction events, e.g. a way to say that the
action of the left mouse button depends on whether the Shift key is down or not.

\section{Minor things}

\begin{enumerate}
\item Automatically include svn revision number in DESCRIPTION file.
\item Handle device failures better, e.g. on a Mac, try X, on Unix, die gracefully.
\item Shiny transparent objects aren't rendered properly.  E.g. white highlights make
a red sheet clear.  
\item Could we put a viewport in an MDI window?

\end{enumerate}

\end{document}





